An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
minor tweak
added questions

\begin{itemize}
  \item Analogy: programming vs.\ learning to play a musical instrument
  \item Larger assignment (like SIGCSE {\em Nifty Assignments}) :: Recital piece
  \item Short exercise :: Playing a scale
\end{itemize}

@@

>>>>

\begin{itemize}
  \item Analogy: learning programming vs.\ learning to play a musical instrument
  \item Larger assignment (like SIGCSE {\em Nifty Assignments}) :: Recital piece
  \item Short exercise :: Playing a scale
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item What experiments should we do to find out?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises to use?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}
